---
title: "Ex02_tasks"
author: "Xingyu.Hu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

1. calculate 1+2+3+...+100

```{r}
sum(1:100)
```

2. y=exp(ax)+b, a=3.2, b=98. Calculate the y values when x=0.2, 2, 20, 200

```{r}
exp_y <- function(a, b, x) {
    exp(a * x) + b
}
exp_y(3.2, 98, 0.2)
exp_y(3.2, 98, 2)
exp_y(3.2, 98, 20)
exp_y(3.2, 98, 200)
```

The air quality dataset was introduced in Week1. Download it from LMO and import it into R. This and the subsequent tasks will do some analysis based on this dataset.

1. How many rows and columns does this data frame have?

```{r}
df_aq <- read.csv("Data/airquality.csv")
cat("Numbers of rows: ", nrow(df_aq))
cat("Numbers of columns: ", ncol(df_aq))
```

2. What was the temperature on June 22?

```{r}
cat("The temperature is: ", df_aq[with(df_aq, Month==6 & Day==22), 'Temp'])
```

3. What was the mean early afternoon ozone concentration (ppb) in June?

```{r}
mean(df_aq[df_aq$Month==6, "Ozone"], na.rm=TRUE)
```

4. What was the mean, maximum, minimum, median of the morning wind speed in the whole dataset?

```{r}
cat("Mean = ", mean(df_aq$Wind))
cat("Maximum = ", max(df_aq$Wind))
cat("Minimum = ", min(df_aq$Wind))
cat("Median = ", median(df_aq$Wind))
summary(df_aq$Wind)
```

5. The temperature in the dataset was given in F. Add a new column for the temperature in C.

```{r}
Celsius <- round((df_aq$Temp - 32) / 1.8)
df_aq$Celsius <- Celsius
```

6. Save the frame as a .csv file.

```{r}
write.csv(df_aq, "Data/airquality_new.csv", row.names = FALSE)
```

The ENV211 Students dataset was introduced in Week 1. Download it from LMO and import it into R. This and the subsequent tasks will do some analysis based on this dataset.

1. How many rows and columns does this data frame have?

```{r}
stud <- read.csv("Data/students_env221.csv")
cat("Numbers of rows: ", nrow(stud))
cat("Numbers of columns: ", ncol(stud))
```

2. What is the hometown of the student No. 16?

```{r}
stud[stud$ID==16, "HOME"]
```

3. What is the mean height of male and female students, respectively?

```{r}
cat("Average height of male student: ", mean(stud[stud$GENDER=="Male", "HEIGHT"]))
cat("Average height of female student: ", mean(stud[stud$GENDER=="Female", "HEIGHT"]))
tapply(stud$HEIGHT, stud$GENDER, mean)
```

4. What is the mean, maximum, minimum, median of the shoe size in the whole dataset?

```{r}
cat("Mean = ", mean(stud$SHOE))
cat("Maximum = ", max(stud$SHOE))
cat("Minimum = ", min(stud$SHOE))
cat("Median = ", median(stud$SHOE))
summary(stud$SHOE)
```

5. How many students knew nothing about statistics? How about R?

```{r}
cat(sum(stud$STAT=="1. I know nothing about it.", na.rm=TRUE), 
    " and ", 
    sum(stud$R=="1. I know nothing about it.", na.rm=TRUE), 
    " students knew nothing about statistics and R, respectively.")
```

6. Body mass index (BMI) is a measure of body fat based on height and weight that applies to adult men and women. Add a new column as the BMI.

```{r}
BMI <- round(stud$WEIGHT / (stud$HEIGHT / 100) ^ 2, 1)
stud$BMI <- BMI
```

7. Save the data frame as a .csv file.

```{r}
write.csv(stud, "Data/students_ENV221_new.csv", row.names = FALSE)
```

