---
title: "Ex03_tasks"
author: "Xingyu.Hu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

The Iris dataset was introduced in Lecture 1. Import it into R. This and the subsequent tasks will do some analysis based on this dataset.

1. Insert a column named "petal_length_level" in the iris data, showing whether the petal length is greater than 4. Two values in this column: "< 4", ">= 4".

```{r}
iris$petal_width_level <- ifelse(iris$Petal.Length < 4,
                                 '< 4',
                                 '>= 4')
```

---

2. Insert a column named "sepal_length_level" in the iris data, showing whether the sepal width is greater or smaller than 3. Three values in this column: "< 3", "= 3", "> 3"

```{r}
iris$sepal_width_level <- ifelse(iris$Sepal.Width > 3, 
                                 '> 3', 
                                 ifelse(iris$Sepal.Width == 3, 
                                        '= 3', 
                                        '> 3'))
```

---

3. Use the loop function: cut the iris data frame into three data frames based on the three kinds of iris species, and save each of them in a ".csv" file.

```{r}
setosa <- data.frame()
versicolor <- data.frame()
virginica <- data.frame()

for(i in 1:nrow(iris)){
    if(iris$Species[i] == 'setosa'){
        setosa <- rbind(setosa, iris[i,])
    } else if(iris$Species[i] == 'versicolor'){
        versicolor <- rbind(versicolor, iris[i,])
    } else if(iris$Species[i] == 'virginica'){
        virginica <- rbind(virginica, iris[i,])
    }
    
    if(i == nrow(iris)){
        write.csv(setosa, 'setosa.csv')
        write.csv(versicolor, 'versicolor.csv')
        write.csv(virginica, 'virginica.csv')
    }
}
```

---

4. Body mass index (BMI) is a measure of body fat based on height and weight tha applies to adult men and women. Create a self-defined function for calculating BMI from the height and weight.

```{r}
bmi <- function(height, weight){
    x <- weight / height ^ 2
    return(x)
}
```

---

5. Apply this function to the ENV221 students dataset and add a new column for the BMI values.

```{r}
df_stud <- read.csv("Data/students_env221.csv")
df_stud$BMI <- bmi(df_stud$HEIGHT/100, df_stud$WEIGHT)
```

---

6. Install the MSG package from GitHub ("yihui/MSG")

```{r}
library(remotes)
install_github("yihui/MSG")
```

---

7. What can MSG used for?

```{r}
??MSG
# Datasets and functions for the Chinese book “Modern Statistical Graphics”.
```

---

8. How popular is MSG?

```{r}
library(beginr)
beginr::plotpkg("MSG")
```

---

9. What is the function msg() used for?

```{r}
??msg()
# Plot a graph with a pre-installed R script
```

---

10. Who are the authors of MSG? Can you search the internet for more information of them?

```{r}
# https://yihui.org/
```

---

11. Give the citation of the MSG package.

```{r}
citation('MSG')
# Xie Y, Zhao P (2022). _MSG: Data and Functions for the Book Modern Statistical Graphics_. R package version 0.8.1, <https://github.com/yihui/MSG>.
```







