---
title: "Ex04_tasks"
author: "Xingyu.Hu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(GGally)
```

---

The Air Quality dataset was introduced in Lecture 1. Import it into R. This and the subsequent tasks will do some analysis based on this dataset. 

1. Make a boxplot of the early afternoon ozone concentration in June.

```{r}
boxplot(airquality[airquality$Month == 6, 1],
        main = "Boxplot of the early afternoon ozone concentration in June",
        ylab = "Ozone Concentration (ppb)")

ozone_boxplot <- ggplot(airquality[airquality$Month == 6,]) + 
    geom_boxplot(aes(Ozone)) +
    labs(title = "Boxplot of the early afternoon ozone concentration in June",
         x ="Ozone Concentration (ppb)")

ozone_boxplot
```

---

2. Make a histogram of the early afternoon ozone concentration in June.

```{r}
hist(airquality[airquality$Month == 6, 1],
     main = "Histogram of the early afternoon ozone concentration in June",
     xlab = "Ozone Concentration (ppb)")

ozone_histogram <- ggplot(airquality[airquality$Month == 6,]) +
    geom_histogram(aes(Ozone)) +
    labs(title = "Histogram of the ealy afternoon ozone concentration in June",
         x = "Ozone Concentration (ppb)", 
         y = "Frequency")

ozone_histogram
```

---

3. Save the boxplot and histogram as .pdf files.

```{r}
ggsave("Ozone_boxplot.pdf", ozone_boxplot, path = 'Graphs')
ggsave("Ozone_histrogram.pdf", ozone_histogram, path = 'Graphs')
```

---

The ENV221 Students dataset was introduced in Lecture 2. Import it into R. This and subsequent tasks will do some analysis based on this dataset.

1. Make a scatter plot for the weight against the height.

```{r}
stud <- read.csv('Data/students_env221.csv')

stud_weight_height_scatter <- ggplot(stud, aes(x = HEIGHT, y = WEIGHT)) +
                                geom_point() +
                                geom_smooth(method = "lm") +
                                labs(title = "Relation between weight and height",
                                     x = "Height /cm",
                                     y = "Weight /kg")

stud_weight_height_scatter
```

---

2. Make histograms of the BMI for the female and male students, respectively.

```{r}
stud_new <- read.csv('Data/students_ENV221_new.csv')

male_bmi <- ggplot(stud_new[stud_new$GENDER == 'Male',]) +
                geom_histogram(aes(BMI)) + 
                labs(title = "BMI of male students",
                     y = "Frequency")

male_bmi

female_bmi <- ggplot(stud_new[stud_new$GENDER == 'Female',]) +
                geom_histogram(aes(BMI)) + 
                labs(title = "BMI of female students",
                     y = "Frequency")

female_bmi
```

---

3. Make a bar plot of the number of the students at different levels in Statistics and R.

```{r}
stat_bar <- ggplot(stud) +
                geom_bar(aes(STAT)) +
                labs(title = "Number of the students at different levels in Statistics",
                     x = "Knowledge Level",
                     y = "Frequency")

stat_bar

r_bar <- ggplot(stud) + 
            geom_bar(aes(R)) +
            labs(title = "Number of the students at different levels in R",
                 x = "Knowledge Level",
                 y = "Frequency")

r_bar
```

---

4. Make a pair plot of all the numeric variables in the dataset.

```{r}
numeric_pairs <- ggpairs(stud_new[, c(4, 5, 6, 11)], 
                         aes(colour = stud$GENDER, alpha = 0.5))
```

---

5. Save the graph as .pdf files.

```{r}
ggsave('stud_weight_height_scatter.pdf', 
       stud_weight_height_scatter, 
       path = 'Graphs')

ggsave('male_bmi.pdf', male_bmi, path = 'Graphs')
ggsave('female_bmi.pdf', female_bmi, path = 'Graphs')

ggsave('stat_bar.pdf', stat_bar, path = 'Graphs')
ggsave('r_bar.pdf', r_bar, path = 'Graphs')

ggsave('numeric_paris.pdf', numeric_pairs, path = 'Graphs')
```










