---
title: "Ex06_tasks"
author: "Xingyu.Hu"
date: "2022-10-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The airquality dataset was introduced in Lecture 1. Import it into R. This and the subsequent tasks will do some analysis based on this dataset.

1. Describe the wind speed (in km/hour) with the center, spread and shape.

```{r}
# Center
summary(airquality$Wind)
# Spread
range(airquality$Wind)
var(airquality$Wind)
sd(airquality$Wind)
# Shape
library(e1071)
skewness(airquality$Wind)
kurtosis(airquality$Wind)
```

- Positively Skewed

---

2. Draw a strip chart, a histogram, a box plot, and a violin plot for all the observations of wind speed. Are there outliers? How do you know it? If there are, what time was it when they happened?

```{r}
stripchart(airquality$Wind, method = "jitter", jitter = 0.1)
boxplot(airquality$Wind)

library(ggplot2)
ggplot(airquality, aes(x = as.character(Month), y = Wind)) +
    geom_violin() +
    geom_boxplot(width = 0.1)

IQR(airquality$Wind)
outlierQ1 <- 7.4 - 1.5 * 4.1
outlierQ3 <- 11.5 + 1.5 * 4.1
airquality[airquality$Wind > outlierQ3 | airquality$Wind < outlierQ1,]

```

- From the box plot, three outliers can be found.

---

3. Give each wind speed observation an international description.

```{r}
airquality$Wind_desc <- ifelse(airquality$Wind < 1, "Calm",
                        ifelse(airquality$Wind >= 1 & airquality$Wind < 6, "Light Air",
                        ifelse(airquality$Wind >= 6 & airquality$Wind < 12, "Light Breeze",
                        ifelse(airquality$Wind >= 12 & airquality$Wind < 20, "Gentle Breeze",
                        ifelse(airquality$Wind >= 20 & airquality$Wind < 29, "Moderate Breeze",
                        ifelse(airquality$Wind >= 29 & airquality$Wind < 39, "Fresh Breeze",
                        ifelse(airquality$Wind >= 39 & airquality$Wind < 50, "Strong gale",
                        ifelse(airquality$Wind >= 50 & airquality$Wind < 62, "Fresh Breeze",
                        ifelse(airquality$Wind >= 62 & airquality$Wind < 75, "Fresh gale",
                        ifelse(airquality$Wind >= 75 & airquality$Wind < 89, "Stong gale",
                        ifelse(airquality$Wind >= 89 & airquality$Wind < 103, "Whole gale",
                        ifelse(airquality$Wind >= 103 & airquality$Wind < 117, "Storm", "Hurricane"))))))))))))
```

---

4. Draw a pie chart for the frequency of the wind description.

```{r}
pie(table(airquality$Wind_desc))
```
---

5. Make a contingency table for the wind description and the month. How many observations of Modern Breeze can you find in July?

```{r}
table(airquality$Wind_desc, airquality$Month)
```

- 0 "Modern Breeze" in July.