---
title: "Ex07_tasks"
author: "Xingyu.Hu"
date: "2022-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

In an experimental pond, there are three species of fish, named as A, B, and C, with the quantity of 1000 for each. The lengths of them are 1 cm, 2 cm, and 3 cm, respectively. Each fish has the equal opportunity to be taken in a random sample. This and the subsequent tasks will do some analysis based on this dataset.

1. What is the distribution of all the fishes' length as the population? Plot a histogram. Give the population mean and standard deviation for the length.

```{r}
species <- rep(c('A', 'B', 'C'), times = c(1000, 1000, 1000))
length <- rep(c(1, 2, 3), times = c(1000, 1000, 1000))
fish <- data.frame(species, length)

hist(fish$length)
mean(fish$length)
sd(fish$length * sqrt(nrow(fish)-1 / nrow(fish)))
```

---

2. You randomly select a sample of 3 fishes from the population and you record the lengths of them (e.g. 1 cm, 1 cm, 3 cm) and calculate the mean (e.g. 5/3 = 1.67 cm)

- How many possible samples could you get?
- List all possible samples (e.g. 1, 1, 1; 1, 1, 2; 1, 1, 3; ...) in a table
- Show the sample distribution of the mean in a table and in a histogram.
- Calculate the standard error of the mean according to the population mean and sample size. Compare it with the standard deviation of the sample distribution of the mean.

```{r}
choose(3000,3)
# answer: 4495501000   

samplen <- replicate(100, sample(length, 3))
sample_mean <- apply(samplen, 2, mean)
hist(sample_mean, freq = FALSE)

se <- sd(sample_mean) * sqrt((100 - 1) / 100)
se
sd(sample_mean)
```

---

3. What is the probability of sampling 3 fishes with a mean length > 1.67 cm?

```{r}
p1 <- pnorm(1.67, mean = mean(samplen), sd = se)
p <- 1-p1
p
```

4. You randomly select a sample of 30 fishes from the population and you record the lengths of them and calculate the mean.

- How many possible samples could you get?
- Show the (approximate) sample distribution of the mean in a histogram.
- Calculate the standard error of the mean according to the population mean and sample size. Compare it with the standard deviation of the sample distribution of the mean.

```{r}
choose(3000,30)
# answer:6.711158e+71

samplen <- replicate(100, sample(fish$length, 30))
sample_mean <- apply(samplen, 2, mean)
hist(sample_mean, freq = FALSE)

se<-sd(sample_mean) * sqrt((100 - 1) / 100)
se
sd(sample_mean)
```

---

5. What is the probability of sampling 30 fishes with a mean length > 1.67 cm?

```{r}
p1 <- pnorm(1.67, mean = mean(samplen), sd = se)
p <- 1-p1
p
```

---

Download the data file twopeasks.csv from the Learning Mall. We assume it is the population of a certain environmental variable. This and the subsequent tasks will do some analysis based on this dataset.

6. Plot a histogram of this variable. It is a normal distribution? Why?

```{r}
twopeaks <- read.csv("Data/twopeaks.csv")
hist(twopeaks$data, 
     las = 1, freq = FALSE)
# No, mean is not equal mediean.
```

---

7. You randomly select a sample from the population. If the sample size is 3, how many possible samples could you get? Show the (approximate) sample distribution of the mean in a histogram. Is it a normal distribution? Why?

```{r}
choose(20000,3)
# answer:1.333133e+12

samplen <- replicate(500, sample(twopeaks$data, 3))
sample_mean <- apply(samplen, 2, mean)
hist(sample_mean, freq = FALSE)

# No, it has multiple peaks.
```

