---
title: "Ex10_tasks"
author: "Xingyu.Hu"
date: "2022-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The Iris dataset was introduced in Lecture 1. Import it into R. This and the subsequent tasks will do some analysis based on this dataset.

1. Give the reproducible R codes for constructing scatter plots of the sepal length against the width, and the petal length against the petal width, for each species separately, each with a simple linear-regression line.

```{r message=FALSE}
library(ggplot2)
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) +
    geom_point() + 
    facet_wrap(~ Species, scales = 'free_x') +
    geom_smooth(method='lm', formula = y ~ x) +
    theme_classic()

ggplot(iris, aes(x = Petal.Length, y = Petal.Width)) +
    geom_point() + 
    facet_wrap(~ Species, scales = 'free_x') +
    geom_smooth(method = 'lm', formula = y ~ x) +
    theme_classic()
```

---

2. Calculate the correlation coefficients between the sepal length and width, and the petal length and width for each species separtely, step by step.

```{r message=FALSE}
library(dplyr)
mean_iris <- iris %>% group_by(Species) %>%
    summarise(Sepal.Length = mean(Sepal.Length),
              Sepal.Width = mean(Sepal.Width),
              Petal.Length = mean(Petal.Length),
              Petal.Width = mean(Petal.Width)) %>%
    data.frame()

sd_iris <- iris %>% group_by(Species) %>%
    summarise(Sepal.Length = sd(Sepal.Length),
              Sepal.Width = sd(Sepal.Width),
              Petal.Length = sd(Petal.Length),
              Petal.Width = sd(Petal.Width)) %>%
    data.frame()

cor_iris <- function(species = 'setosa', x = 'Sepal.Length', y = 'Sepal.Width'){
    n <- 50
    co <- 1 / (n - 1) * 
        sum((iris[iris$Species == species, x] - mean_iris[mean_iris$Species == species, x]) * 
                (iris[iris$Species == species, y] - mean_iris[mean_iris$Species == species, y]))
    r <- co / (sd_iris[sd_iris$Species == species, x] * sd_iris[sd_iris$Species == species, y])
}

setosa_sepal <- cor_iris('setosa', 'Sepal.Length', 'Sepal.Width')
setosa_petal <- cor_iris('setosa', 'Petal.Length', 'Petal.Width')
versicolor_sepal <- cor_iris('versicolor', 'Sepal.Length', 'Sepal.Width')
versicolor_petal <- cor_iris('versicolor', 'Petal.Length', 'Petal.Width')
virginica_sepal <- cor_iris('virginica', 'Sepal.Length', 'Sepal.Width')
virginica_petal <- cor_iris('virginica', 'Petal.Length', 'Petal.Width')

cor <- data.frame(c(setosa_sepal, setosa_petal, versicolor_sepal, versicolor_petal, virginica_sepal, virginica_petal))
colnames(cor) <- "correlation coefficient"
rownames(cor) <- c("setosa_sepal", "setosa_petal", "versicolor_sepal", "versicolor_petal", "virginica_sepal", "virginica_petal")
cor
```

---

3. Are the correlation coefficients for the population zero? Do the hypothesis test step by step.

- **Hypothesis:**
    - $H_0:\rho=0$
    - $H_1:\rho\ne0$
    
```{r}
corp_test <- function(r = 1, n = 50){
    t_score <- r * sqrt((n - 2) / (1 - r ^ 2))
    t_critical <- qt(0.975, df = n - 2)
    p <- pt(t_score, df = n - 2, lower.tail = FALSE) * 2
    decision <- ifelse(p < 0.05, 'Reject H0', 'Fail to reject H0')
    return(c(t_score, t_critical, p, decision))
}

iris_test <- sapply(cor[, 1], corp_test)
rownames(iris_test) <- c("t_score", "t_critical", "p-value", "Decision")
colnames(iris_test) <- c("setosa_sepal", "setosa_petal", "versicolor_sepal", "versicolor_petal", "virginica_sepal", "virginica_petal")
iris_test
```

---

A scientist assumes that the temperature (the explanatory variable) is a good predictor of plant height (the response variable), and the logarithm of the plant height linearly depends on the temperature. She collects a data set as Plant_height.csv. Download the dataset from LMO. This and the subsequent tasks will do some analysis based on this dataset.

1. Make a scatter plot of the logarithm of the plant height (loght) against the temperature (temp). Heightlight the means.

```{r}
plant <- read.csv("../Data/Plant_height.csv")

ggplot(plant, aes(x = temp, y = loght)) +
    geom_point() +
    geom_point(aes(x = mean(temp), y = mean(loght)), colour = "red", size = 2.5) +
    labs(x = "Temperature", y = "Log(plant height)") +
    theme_classic()
```

---

2. Apply the simple linear regression model and get the intercept and slope for the regression line.

```{r}
mean_loght <- mean(plant$loght)
mean_temp <- mean(plant$temp)

b <- sum((plant$loght - mean_loght) * (plant$temp - mean_temp)) / 
    sum((plant$temp - mean_temp) ^ 2)
a <- mean_loght - b * mean_temp

c(a, b)
```

---

3. Do the hypothesis test about the fit step by step.

- $H_0:$ There is no relationship between the height and the shoe size.
- $H_1:$ There is relationship between the height and the shoe size.

```{r}
# Gather data
dtf <- data.frame(loght = plant$loght, temp = plant$temp)
dtf$predicated <- a + b * dtf$temp
dtf$residual <- dtf$loght - dtf$predicated

# Calculate a test statistic: F-test
## df
n <- nrow(dtf)
dftot <- n - 1
dfres <- n - 2
dfreg <- 1

## ss
sstot <- sum((dtf$temp - mean_temp) ^ 2)
ssres <- sum((dtf$loght - dtf$predicated) ^ 2)
ssreg <- sum((dtf$predicated - mean_loght) ^ 2)

## ms
msreg <- ssreg / dfreg
msres <- ssres / dfres

## f
f_score <- msreg / msres
f_critical <- qf(0.05, df1 = dfreg, df2 = dfres, lower.tail = FALSE)
p_value <- pf(f_score, df1 = dfreg, df2 = dfres, lower.tail = FALSE)
c(f_score, f_critical, p_value)
```

- **Reject $H_0$. There is relationship between the temperature and tree height.**

---

4. Do the hypothesis test about the slope step by step.

- $H_0:\beta=0.$ The slope of the regression line is zero. 
- $H_1:\beta\ne0.$ The slop of the regression line is not zero.

```{r}
# Calculate a test statistic: t-test
syx <- sqrt(sum(dtf$residual ^ 2) / (nrow(dtf) - 2))
sx <- sd(dtf$temp)
sb <- syx / (sx * sqrt(n - 1))
beta <- 0

t_score <- (b - beta) / sb
t_critical <- qt(0.975, df = n - 1)
p_value <- pt(t_score, df = n - 2, lower.tail = FALSE) * 2
c(t_score, t_critical, p_value)
```

- **Reject $H_0$. The slope of the regression line is not equal to 0.**

---

5. Do the hypothesis test about the intercept step by step.

- $H_0:\alpha=0.$ The intercept of the regression line is zero.
- $H_1:\alpha\ne0.$ The intercept of the regression line is not zero.

```{r}
# Calculate a test statistic: t-test
xbar <- mean_temp
sa <- syx * sqrt(1 / n + xbar ^ 2 / ((n - 1) * sx ^ 2))
alpha <- 0

t_score <- (a - alpha) / sa
t_critical <- qt(0.975, df = n -1)
p_value <- pt(t_score, df = n - 2) *2
c(t_score, t_critical, p_value)
```

- **Reject $H_0$. The intercept of the regression line is not equal to 0.**

---

6. Visualize the simple linear regression in the graph.

```{r}
ggplot(plant, aes(x = temp, y = loght)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ x) +
    geom_point(aes(x = mean(temp), y = mean(loght)), colour = "red", size = 2.5) +
    labs(x = "Temperature", y = "Log(plant height)") +
    theme_classic()
```




